### 2020-06-08 README.Rmd
certain winds to certain wind speed close parentheses

In addition to giving the names and closest dates of each storm for each county (`closest_date`-- note, this is given based on local time for the county; see documentation for the [`countytimezones` package](https://cran.r-project.org/web/packages/countytimezones/index.html) to find out more about how local time was calculated from UTC for each county), this function also gives you the distance between the county and the storm's track at the time when the storm was closest to the county's population weighted center (`storm_dist`, in kilometers) and the total precipitation over the included days (`tot_precip`). The returned dataframe also gives the time of closest approach in both local time (`local_time`) and UTC (`closest_time_utc`), based on 15-minute intervals along the storm's track.

>>>>

In addition to giving the names and closest dates of each storm for each county (`closest_date`) -- note, this is given based on local time for the county; see documentation for the [`countytimezones` package](https://cran.r-project.org/web/packages/countytimezones/index.html) to find out more about how local time was calculated from UTC for each county), this function also gives you the distance between the county and the storm's track at the time when the storm was closest to the county's population weighted center (`storm_dist`, in kilometers) and the total precipitation over the included days (`tot_precip`). The returned dataframe also gives the time of closest approach in both local time (`local_time`) and UTC (`closest_time_utc`), based on 15-minute intervals along the storm's track.
